\documentclass{article}

\usepackage{titlesec} %for titleformat
\usepackage{titling} %for renewcommand
\usepackage[margin=.5in]{geometry} %for margins
\usepackage{setspace}
\usepackage{pifont} %to little rating stars
\usepackage{fontawesome} %to web icons
\usepackage[utf8]{inputenc} % for accentuation
%\usepackage[T1]{fontenc}

\titleformat{\section} %{command}[shape]
{\LARGE\tt\lowercase} %format
{} %label
{0em} %sep (is the horizontal separation between label and title body and it must be a length and not be empty)
{}[\titlerule] %{before code}[after code]  is code preceding/following the title body
% to check the options: https://www.overleaf.com/learn/latex/Sections_and_chapters

\titleformat{\subsection}
{\sf\large}
{$\bullet$} %dist from the margin ex.: {\hspace{.25in}}
{1em} %dist from the bullet to text
{}[]

\titleformat{\subsubsection}[runin]
{\sf\normalsize}
{}
{0em}
{}[]

\titlespacing{\subsubsection}
{0em}{.5em}{1em} %{dist to the margin}{between the subsubs}{runin}


\renewcommand{\maketitle}{
    \begin{raggedleft}
    {\Huge\bfseries\theauthor}

    \vspace{.25em}
    \large{\emph{A passionate technology student who used to trade assets in banks}}\

    \vspace{.25em}
    +55 11 97414-3200 $|$ carime@gmail.com $|$  \faLinkedin\  \ /carimebumaruf

    \end{raggedleft}
}

\begin{document}


\title{Carime Bumaruf}
\author{Carime Bumaruf}

\maketitle

\vspace{2.5mm} %2,5mm vertical space

\section{Nice to Meet You!}
\begin{spacing}{1.1}

    I'm intending to become a ``Y tech professional'', that one with a good balance between
    soft and hard skills. Better saying, I'm eager to combine my previous business 
    experience as a banking trader with the knowledge I'm building up as a Computer 
    Science student.   
    The feedback I received working in financial markets highly prized my communication 
    and relational skills as well as my ability to work in so different roles - behind 
    the computer or in a client meeting.

\end{spacing}

\section{Education}
\subsection{Universidade de S\~ao\ Paulo (USP) - S\~ao\ Paulo, Brazil \hfill 2017/2021}
Bachelor's Degree in Computer Science

\subsection{Funda\c{c}\~ao\ Get\'ulio\ Vargas (FGV) - S\~ao\ Paulo, Brazil \hfill 2015/2016}
Postgraduate Program - MBA in Strategic and Economic Project Management

\subsection{Universidade de S\~ao\ Paulo (USP) - S\~ao\ Paulo, Brazil \hfill 2003/2008}
Bachelor's Degree in Physics

\section{Technical Skills}
\subsection[]{Work Flow}
\subsubsection{Git}
\faGithub \  \ /carimeb

\subsection{Languages}
\subsubsection{Programming}
C, Java, Kotlin\   \   \ding{72} , \ding{72}\ding{72}\ding{72}, \ding{72}\ding{72} 

\subsubsection{Scripting}
Python, JavaScript\   \   \ding{72}\ding{72}\ding{72} , \ding{72}

\subsubsection{Markup}
HTML, XML, {\LaTeX}   \   \ding{72}\ding{72} , \ding{72}\ding{72}, \ding{72}\ding{72} 

\subsubsection{Database Management}
SQL, JSON, Cypher   \   \ding{72}\ding{72}\ding{72}, \ding{72}\ding{72}, \ding{72}\ding{72}

\section{Work Experience}
\subsection{Standard Chartered Bank - Sales Trader for Global Corporates \hfill 2012/2014}
I used to sell financial assets and hedge tools to the Brazilian branches of worldwide companies.

\emph{Most valuable transferable skills: LOVE by learning new things and ``tweakable'' communication.}

What I really liked about this job: cross-departmental collaborative work and knowledge sharing.

\subsection{HSBC Bank Brasil - Fixed Income Trader and Sales Trader for Small Local Companies \hfill 2007/2012}
Firstly as an intern, then as fixed income trader for Brazilian bonds and finally as foreign exchange sales evangelist.

\emph{Skills I acquired I am most proud: high resilience, self-taught and enthusiasm to changes.}



\end{document}